\section{Exposure to the Industry}

The training period I spent at vcLABs can be considered as one of the greatest experience that I was able to gain being an  undergraduate of University of Moratuwa. I had the opportunity to work with a group of people who are wonderful. They helped me to survive in the competitive nature in the industrial training.

I think learned lots of lessons about my self during the time period. Following are some areas I think I improved in the training period.

\begin{itemize}
\item Work with a group
\subitem Although I thought working in a group is not much of a task, I figured out that it was not so. In an competitive environment one should be careful to gain success with team spirit
\subitem Every person has their own point of view. So it is important to respect that. As a team, people should consider every choice and come up with the best solution. Everyone should encourage such behavior.

\item Meeting deadlines
\subitem In an competitive environment, the idea of deadlines makes a huge effect. So the importance of meeting deadlines should be significant in order to achieve success in career.

\item Punctuality 
\subitem The office hours of vcLABs was from 9 am to 5 pm. But it was tradition to work from 8 am. This was a life lesson to me

\item Respect Company traditions and work ethics
\subitem Although a small company vcLABs had its own set of tradition. We didn't call one another "Sir" or "Miss" but with the first names. I think that bond between the crew made it a great one.

\item Relationship with a third party
\subitem As vcLABs is a service provider for DialogTV, they kept their relationship DialogTV in a certain way.
\end{itemize}

In technical aspects, I think I had an immense transformation in that regard during the 24-week time period. I made my self  aware of lots of software tools and techniques that sharpened my knowledge about those too. Working in research is in a way much more enjoyable than routine work because every day one find new purpose. Getting a practical and applicable knowledge about the scientific method was also fun and enjoyable.

In this training period I got to know what its actually meant by scientific thinking. Although I regret a little that I could worked harder in the training period, I think the experience I gained is definitely going to live with me every day to make my career more successful.

\section{Comments and Suggestions to the Training Program}
I think the training program is essential for an undergraduate to assess himself on the fact that they are suitable to the existing industry that they are going practice in the future. We gain knowledge about academic things in the university, but, application of academic knowledge is somewhat different from what one would expect. So this is a great opportunity to everyone to witness that difference.

After the training period, the student is given another year to work on to survive in the industry more effectively. I think that is also necessary in order to see a difference in an graduate.